\documentclass[11pt,a4paper,roman]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{blue}
\nopagenumbers{}

\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage{tikz}
\usepackage{url}
\usepackage{amsmath}

\usepackage[scale=0.84]{geometry}
\usepackage{multicol}

\usepackage{import}

\name{\href{https://elias-ramzi.github.io/}{Elias Ramzi}}{\color{gray} | \LARGE{ AI Research Scientist} }
\address{Paris, France}{}{}

\newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l}
    {\bfseries #4}
  \end{tabular}
  \hfill%
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular} \\
  \begin{tabular}{@{}l}
    {\itshape #3}
  \end{tabular}
  \hfill%
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\customcvproject}[4][.25em]{
  \begin{tabular}{@{}l}
    {\bfseries #2}
  \end{tabular}
  \hfill%
  \begin{tabular}{l@{}}
     {\itshape #3}
  \end{tabular}
  \ifx&#4&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\skillgroup}[2]{%
  \par\addvspace{.5em}{\bfseries #1}\par\nopagebreak
  {\small #2}\par\addvspace{.3em}}

\setlength{\tabcolsep}{12pt}
\setlength{\emergencystretch}{3em}

\newcommand{\ExternalLink}{%
    \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{%
        \begin{scope}[x=1ex, y=1ex]
            \clip (-0.1,-0.1)
                --++ (-0, 1.2)
                --++ (0.6, 0)
                --++ (0, -0.6)
                --++ (0.6, 0)
                --++ (0, -1);
            \path[draw,
                line width = 0.5,
                rounded corners=0.5]
                (0,0) rectangle (1,1);
        \end{scope}
        \path[draw, line width = 0.5] (0.5, 0.5)
            -- (1, 1);
        \path[draw, line width = 0.5] (0.6, 1)
            -- (1, 1) -- (1, 0.6);
        }
    }

\begin{document}

\makecvtitle
\vspace*{-23mm}

\begin{center}
\begin{tabular}{ c c c c }
 \faEnvelopeO\enspace \href{mailto:elias.ramzi@gmail.com}{elias.ramzi@gmail.com} & \faMobile\enspace+33\enspace6 28 25 40 88 &    \faGithub\enspace \href{https://elias-ramzi.github.io/}{elias-ramzi} & \faGraduationCap\enspace \href{https://scholar.google.com/citations?user=mbfTD_UAAAAJ}{Google Scholar} \\
\end{tabular}
\end{center}

\begin{center}
\textbf{End-to-end driving --- planning, world models, and multimodal LLMs}
\end{center}


\section{Experiences}

{\customcvproject{valeo.ai (Paris, France) - full-time}{2024-}{
\textit{AI research scientist}\\
Deep learning research interests: end-to-end planning, world models, VLMs / LLMs.
\medbreak
\begin{itemize}
\item Developed world models for autonomous driving, leading to VaViM/VaVAM (technical report, CoRL Workshop).
\medbreak
\item Co-supervising two PhD students: one on LLMs and VLMs (ICLR 2025, ACL Findings 2026), another on world models and RL.
\medbreak
\item Scaled training of generative models up to 1.9B parameters across 192 H100s using $\mu$P and DeepSpeed ZeRO-2.
\medbreak
\end{itemize}
}

{\customcvproject{Cnam \& Coexya (Paris, France) - 3 year PhD}{2021-2024}{
\textit{PhD student}\\
PhD focused on computer vision and image retrieval:
\medbreak
\begin{itemize}
    \item Designed novel ranking losses for image retrieval, combining theoretical analysis with large-scale experiments.
    \medbreak
    \item Published four papers in major international machine learning conferences (NeurIPS, ECCV$\times$2, ICML), three of which as first author, and 2 papers in journals (TPAMI, TMLR).
    \medbreak
    \item Transferred HAPPIER (ECCV) to trademark logo retrieval; the resulting models were deployed in production in Coexya's Acsepto product in 2024.
    \medbreak
    \item Ran distributed training experiments across up to 16 GPUs on France's Jean Zay HPC cluster.
    \medbreak
\end{itemize}}
}

{\customcvproject{Cnam (Paris, France) - 5 month internship}{2020}{
\textit{Research intern}\\Deep learning for 3D medical image segmentation. I used a learned confidence measure (ConfidNet) to combine segmentation results from different 2D U-Nets.
}

{\customcvproject{Sancare (Paris, France) - 6 month internship}{2019}{\textit{Data engineer and data scientist intern}
}

 {\customcvproject{Balto (Sydney, Australia) - 6 month internship}{2018}{\textit{Data engineer intern}
 }}


\section{Education}
{\customcvproject{PhD in Computer Science, Cnam \& Coexya (France)}{2021-2024}
  {Ranking losses and hierarchical learning for image retrieval.
  Awarded the ``Prix de Thèse'' by \href{http://afrif.irisa.fr/?page_id=54}{AFRIF \ExternalLink} (June 2025). 6 publications including 4 first-author papers.
  \\Supervisor: \href{https://thome.isir.upmc.fr}{Nicolas Thome \ExternalLink} (Sorbonne Université).
  \\Advisors: \href{https://nicolas.audebert.at/}{Nicolas Audebert \ExternalLink} (IGN); \href{https://clementrambour.github.io}{Clément Rambour \ExternalLink} (Sorbonne Université).
  \\Industrial advisor: \href{https://orcid.org/0009-0006-7254-6178}{Xavier Bitot \ExternalLink} (Coexya).
  }
}
{\customcvproject{Engineering diploma, CentraleSupélec (France)}{2016-2020}
  {Courses in signal processing (sound, image, speech), machine learning, statistical models (estimators, Bayesian learning), data science (data mining, sparse data representation, NLP).}
}


\section{Technical skills}
\skillgroup{Open source projects}{
   \begin{itemize}
   \setlength{\itemsep}{0pt}
   \item Reproduce VaViM and VaVAM (CoRL'25): \href{https://github.com/valeoai/VideoActionModel/}{\faGithub\enspace VideoActionModel}
   \item Global and local prompts for VLMs (ECCV'24): \href{https://github.com/MarcLafon/gallop/}{\faGithub\enspace GalLoP}
   \item Out-of-distribution detection with HEAT (ICML'23): \href{https://github.com/MarcLafon/heatood/}{\faGithub\enspace HEAT}.
   \item Hierarchical landmark dataset (TPAMI): \href{https://github.com/cvdfoundation/google-landmark}{\faGithub\enspace google-landmark} \& \href{https://github.com/elias-ramzi/SupRank}{\faGithub\enspace SupRank}.
   \item Hierarchical image retrieval with HAPPIER (ECCV'22): \href{https://github.com/elias-ramzi/HAPPIER}{\faGithub\enspace HAPPIER}.
   \item Image retrieval with ROADMAP (NeurIPS'21): \href{https://github.com/elias-ramzi/ROADMAP}{\faGithub\enspace ROADMAP}.
 \end{itemize}}

\skillgroup{Technologies}{
   \begin{itemize}
   \setlength{\itemsep}{0pt}
   \item  {My programming language:} Python -- PyTorch, Lightning, NumPy, Hydra, Pandas, Scikit-learn.
   \item  {My work environment :} Linux/macOS + Git + VS Code \& claude-code.
   \item Other tools: \LaTeX, Shell script, SLURM, HyperQueue, Nextflow.
 \end{itemize}}

\skillgroup{Contributions to open-source}{
   \begin{itemize}
   \item PyTorch metric learning: \href{https://github.com/KevinMusgrave/pytorch-metric-learning/pull/303}{\faGithub\enspace pytorch-metric-learning}.
   \item Implementation of Mixture of Experts: \href{https://github.com/davidmrau/mixture-of-experts/pull/14}{\faGithub\enspace mixture-of-experts}.
   \item PyTorch-Lightning: \href{https://github.com/Lightning-AI/lightning/pull/2319}{\faGithub \enspace lightning}.
   \item Universal Image Embeddings: \href{https://github.com/nikosips/Universal-Image-Embeddings/tree/master\#acknowledgements}{\faGithub \enspace  Universal-Image-Embeddings}.
 \end{itemize}}


\section{Miscellaneous}

\begin{itemize}
    \item French is my mother tongue and I speak English at C1 level.
    \medbreak
    \item I enjoy (trail) running, biking and back-country skiing.
\end{itemize}


 \section{Publications}

Yihong Xu, {\'E}loi Zablocki, Yuan Yin, \textbf{Elias Ramzi}, Ellington Kirby, Alexandre Boulch, Matthieu Cord. "TOAD: Test-Time Trajectory Optimization for Autonomous Driving." \textit{arXiv preprint}, 2026. online: \href{https://arxiv.org/abs/2606.07170}{arxiv.org/abs/2606.07170}

 \medbreak

Shashanka Venkataramanan, Valentinos Pariza, Mohammadreza Salehi, Lukas Knobel, Spyros Gidaris, \textbf{Elias Ramzi}, Andrei Bursuc, Yuki M. Asano, "Franca: Nested Matryoshka Clustering for Scalable Visual Representation Learning." \textit{CVPR}, 2026. online: \href{https://arxiv.org/abs/2507.14137}{arxiv.org/abs/2507.14137}

 \medbreak

 Amaia Cardiel, {\'E}loi Zablocki, \textbf{Elias Ramzi}, and Eric Gaussier. "DRIV-EX: Counterfactual Explanations for Driving LLMs." \textit{ACL findings}, 2026. online: \href{https://arxiv.org/abs/2603.00696}{arxiv.org/abs/2603.00696}

  \medbreak

 Florent Bartoccioni, \textbf{Elias Ramzi}, \textit{et al.} "VaViM and VaVAM: Autonomous Driving through Video Generative Modeling" \textit{Technical report \& CoRL workshop}, 2025. online: \href{https://arxiv.org/abs/2502.15672}{arxiv.org/abs/2502.15672}

\medbreak

Amaia Cardiel, {\'E}loi Zablocki, \textbf{Elias Ramzi}, Oriane Sim{\'e}oni, and Matthieu Cord. "LLM-wrapper: Black-Box Semantic Aware Adaptation of Vision-Language Models for Referring Expression Comprehension." \textit{ICLR}, 2025. online: \href{https://arxiv.org/abs/2409.11919}{arxiv.org/abs/2409.11919}

  \medbreak

     \textbf{Elias Ramzi}, Nicolas Audebert, Cl{\'e}ment Rambour, Andr{\'e} Araujo, Xavier Bitot and Nicolas Thome. "Optimization of Rank Losses for Image Retrieval." \textit{TPAMI}, 2025. online: \href{https://arxiv.org/abs/2309.08250}{arxiv.org/abs/2309.08250}

\medbreak

 Marc Lafon, \textbf{Elias Ramzi}, Cl{\'e}ment Rambour, Nicolas Audebert, Nicolas Thome. "GalLoP: Learning Global and Local Prompts for Vision-Language Models." \textit{ECCV}, 2024. online: \href{https://arxiv.org/abs/2407.01400}{arxiv.org/abs/2407.01400}

 \medbreak

Yannis Karmim, \textbf{Elias Ramzi}, Raphaël Fournier S’niehotta, and Nicolas Thome. "ITEM: Improving Training and Evaluation of Message-Passing based GNNs for top-k recommendation." \textit{TMLR}, 2024. online: \href{https://arxiv.org/abs/2407.07912}{arxiv.org/abs/2407.07912}

 \medbreak

  Marc Lafon, \textbf{Elias Ramzi}, Cl{\'e}ment Rambour, Nicolas Thome. "Hybrid Energy Based Model in the Feature Space for Out-of-Distribution Detection." \textit{ICML}, 2023. online: \href{https://arxiv.org/abs/2305.16966}{arxiv.org/abs/2305.16966}

  \medbreak

 \textbf{Elias Ramzi}, Nicolas Audebert, Nicolas Thome, Cl{\'e}ment Rambour, and Xavier Bitot. "Hierarchical Average Precision Training for Pertinent Image Retrieval." \textit{ECCV}, 2022. online: \href{https://arxiv.org/abs/2207.04873}{arxiv.org/abs/2207.04873}

\medbreak

 \textbf{Elias Ramzi}, Nicolas Thome, Cl{\'e}ment Rambour, Nicolas Audebert, and Xavier Bitot. "Robust and Decomposable Average Precision for Image Retrieval." \textit{NeurIPS}, 2021. online: \href{https://arxiv.org/abs/2110.01445}{arxiv.org/abs/2110.01445}


\end{document}
